### 2022-05-06 manuscript.Rmd
Small fixes to the text

# Justify exclusion of @pedrett2020 based on outlier mean age
mean_age_pedrett2020 <- 2.56 * 365.25 # In days
mean_age_pedrett2020_m <- mean_age_pedrett2020 / 30.417 # In months
mean_age_pedrett2020_z <- (mean_age_pedrett2020 - mean(dat$age_mean)) /
  sd(dat$age_mean) # As z score

```

Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria. Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen’s weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]). Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r irr_code_kappa_w$upper`]). Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached. One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles. Another article [@pedrett2020] was excluded because the average age of the infants studied (`r round(mean_age_pedrett2020_m, 1)` months) was almost twice as high as the average age of the next article (`r round(max(dat$age_mean), 1)` months; $z = `r mean_age_pedrett2020_z`$ compared to all articles). We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life. This procedure led to a total of `r descs$n_articles` articles being included in the meta-analysis (Fig. 4).

@@

```{r, tab1, eval=FALSE, include=TRUE}
# Print table for conversion of effect sizes
tibble(
  `Available statistics` = c(
    "(1) Cohen's $d$ and sample size $n$ [@goulet-pelletier2018]",
    "(2) $t$-statistic and sample size $n$",
    "(3) Mean difference $m_\\text{diff}$ and $SD_{m_\\text{diff}}$",
    "(4) Mean looking times per condition and their $SD$s",
    "(5) Mean novelty preference score $m_\\text{pref}$ and its $SD$"
  ),
  `Conversion to standardized mean difference (Hedges' $g$)` = c(
    paste(
      "$df=2(n-1)$",
      "$j=\\frac{\\Gamma(\\frac{1}{2}v)}{\\sqrt{\\frac{v}{2}}\\Gamma(\\frac{1}{2}(v-1))}$",
      "$g=d*j$",
      sep = "\\newline"
    ),
    "$d=\\frac{t}{\\sqrt{n}}$; then (1)",
    "$d=\\frac{m_\\text{diff}}{SD_{m_\\text{diff}}}$, then (1)",
    paste(
      "$SD_\\text{av}=$",
      "$d=\\frac{m_\\text{novel}-m_\\text{familiar}}{}$",
      sep = "\\newline"
    ),
    ""
  )
) %>%
  apa_table(
    caption = "Extracted between-article summary statistics and conversion to effect sizes",
    font_size = "scriptsize", escape = FALSE
  )
```

>>>>

# Justify exclusion of @pedrett2020 based on outlier mean age
descs_pedrett2020 <- list(age_years = 2.56)
descs_pedrett2020 <- within(descs_pedrett2020, {
  age_months <- age_years * 12
  next_largest_age_months <- max(dat$age_mean) / 30.417
  age <- age_years * 365.25
  z <- (age - mean(dat$age_mean)) / sd(dat$age_mean)
})
```

Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria. Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen’s weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]). Interrater agreement for the specific eligibility criteria were `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]). Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached. One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles. Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles). We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life. This procedure led to a total of `r descs$n_articles` articles being included in the meta-analysis (Fig. 4).

@@
